Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-22 PNAS/index.Rnw
Fix paragraphs and rearrange one bit of intro
round x

ggplot(data = res2, aes(x = N, y = overall, color = factor(r), label = rlab)) +
  geom_textline(parse = T, gap = F, straight = F,
                padding = unit(1, "mm"), vjust = 0, linewidth = 1) +
  xlab("Number of comparisons") +
  scale_x_log10(
    breaks = c(1, 1000, 10000, res2sum$N),
    minor_breaks = c((1:9)[-2],10*(3:9), 100*3:9, 1000*1:9)
  ) +
  geom_hline(yintercept = breakpt, linewidth = 1) +
#  geom_label(
#    data = res2sum,
#    aes(x = N, y = breakpt, label = paste0("N == ", round(N))),
#    parse = T, vjust = 1, hjust = 1) +
  geom_segment(data = res2sum,
     aes(x = N, xend=N, y = -Inf, yend=0.9), colour="grey30", linewidth=0.5) +
  geom_line(data = error_res, linetype = 2, linewidth = 0.75) +
  ylab("Probability false positive\n(N comparisons)") +
  ggtitle("# Comparisons and Overall Accuracy") +
  scale_color_discrete("FP Rate for single comparison", guide = 'none') +
  theme_bw() +
  coord_cartesian(ylim = c(0.775, 1.0)) +
  theme(axis.text.y = element_text(hjust = 0.5, vjust = 0.5, angle = 90))

>>>>

ggplot(data = res2, aes(x = N, y = overall, color = factor(r), label = rlab)) +
  geom_textline(parse = T, gap = F, straight = F,
                padding = unit(1, "mm"), vjust = 0, linewidth = 1) +
  xlab("Number of comparisons") +
  scale_x_log10(
    breaks = c(1, 1000, 10000, res2sum$N),
    labels = c("1", "1000", "10000", round(res2sum$N)),
    minor_breaks = c((1:9)[-2],10*(3:9), 100*3:9, 1000*1:9)
  ) +
  geom_hline(yintercept = breakpt, linewidth = 1) +
#  geom_label(
#    data = res2sum,
#    aes(x = N, y = breakpt, label = paste0("N == ", round(N))),
#    parse = T, vjust = 1, hjust = 1) +
  geom_segment(data = res2sum,
     aes(x = N, xend=N, y = -Inf, yend=0.9, color=factor(r)),
     linewidth=0.5) +
  geom_line(data = error_res, linetype = 2, linewidth = 0.75, alpha =0.5) +
  ylab("1 - Probability of false positive\n(N comparisons)") +
  ggtitle("# Comparisons and Overall Accuracy") +
  scale_color_discrete("FP Rate for single comparison", guide = 'none') +
  theme_bw() +
  coord_cartesian(ylim = c(0.775, 1.0)) +
  theme(axis.text.y = element_text(hjust = 0.5, vjust = 0.5, angle = 90))
